\text{Additive drift with tail bounds}

### 2021-10-14 article.tex
remove long expressions with kvantors

Note that $g(0) = 0$, while $E[X] > 0$, therefore, that in any neighborhood of zero we have

$$\forall c > 0 \, \exists \gamma_c > 0 \, \forall \gamma \in (0, \gamma_c) e^{\frac{\gamma^2 c}{2}} < E[e^{\gamma X}],$$

@@

Hence both requirements are feasible, since we have

$$\exists \gamma_0 > 0 \forall \gamma \in (0, \gamma_0) E[e^{\gamma X}] < 1.$$

>>>>

Note that $g(0) = 0$, while $E[X] > 0$, therefore, that in any neighborhood of zero we have that for all \(c>0\) exists \(\gamma_c > 0\)  that for all \(\gamma \in (0, \gamma_c)\)

$$e^{\frac{\gamma^2 c}{2}} < E[e^{\gamma X}],$$

@@

Hence both requirements are feasible, since we have that exists \(\gamma_0\) such that for all \(\gamma \in (0, \gamma_0)\) $E[e^{\gamma X}] < 1.$
